---
title       : Interactive Documents with R
subtitle    : Slidify + Shiny
author      : Marcio Nicolau
job         : Estatístico
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax, bootstrap, quiz, shiny, interactive]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
ext_widgets : {rCharts: [libraries/nvd3]}
---

## Read-And-Delete

1. Edit YAML front matter
2. Write using R Markdown
3. Use an empty line followed by three dashes to separate slides!

--- .class #id 

## Conteúdo

1. Conceitos básicos

a. Momentos
b. Somatório e Produtório
c. Matrizes
d. Operações Básicas

--- &radio
## Question 1

What is 1 + 1?

1. 1
2. _2_
3. 3
4. 4

*** .hint
This is a hint

*** .explanation
This is an explanation


---
## Interactive Chart
```{r echo = FALSE, results = 'asis', warning=FALSE}
require(rCharts)
haireye = as.data.frame(HairEyeColor)
n1 <- nPlot(Freq ~ Hair, group = 'Eye', type = 'multiBarChart',
  data = subset(haireye, Sex == 'Male')
)
n1$print('chart1')
```

--- &interactive
## Interactive Console

```{r opts.label = 'interactive', results = 'asis', warning=FALSE}
require(googleVis)
M1 <- gvisMotionChart(Fruits, idvar = 'Fruit', timevar = 'Year')
print(M1, tag = 'chart')
```

---
## Dynamic Charts

```{r opts.label = 'shiny'}
slidifyUI(
  sidebarPanel(
    selectInput('sex', 'Choose Sex', c('Male', 'Female')),
    selectInput('type', 'Choose Type',
      c('multiBarChart', 'multiBarHorizontalChart')
    )
  ),
  mainPanel(
    tags$div(id = 'nvd3plot', class='shiny-html-output nvd3 rChart')
  )
)
```

--- &interactive

## Interactive Console

```{r opts.label = 'interactive', results = 'asis'}
require(rCharts)
a <- Highcharts$new()
a$chart(type = "spline")
a$series(data = c(1, 3, 2, 4, 5, 4, 6, 2, 3, 5, NA), dashStyle = "longdash")
a$series(data = c(NA, 4, 1, 3, 4, 2, 9, 1, 2, 3, 4), dashStyle = "shortdot")
a$legend(symbolWidth = 80)
a$print('chart3')
```

--- &interactive

## Results = Markup

```{r opts.label = 'interactive', results = 'markup'}
require(xtable)
options(xtable.type = 'html')
xtable(head(mtcars))
```



